
\documentclass{article} % For LaTeX2e
\usepackage{template/iclr2026_template/iclr2026_conference}
\usepackage{times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}


\title{Complex-Valued CNNs for fastMRI Knee Reconstruction: A Tiny Reproduction}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Anonymous Authors \\
Anonymous Institution \\
\texttt{anonymous@tinyreproductions.edu}}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

% Outline content placeholder until sections are populated.

\begin{abstract}
\textbf{Motivation.} Rapid MRI requires aggressive undersampling, but zero-filled reconstructions yield ringing and blur. \textbf{Goal.} Reproduce the key claim of \citet{cole2020analysisdeepcomplexvaluedconvolutional}: capacity-matched complex-valued CNNs outperform real-valued CNNs on accelerated single-coil knee data. \textbf{Approach.} fastMRI single-coil knee dataset, equispaced undersampling with ACS, complex U-Net vs. real U-Net, identical training/evaluation protocols. \textbf{Findings.} Outline planned quantitative comparison (PSNR/SSIM/L1 deltas), qualitative improvements, and reproducibility contributions. (Will be replaced with final summary.)
\end{abstract}

\input{sections/00_introduction}
\input{sections/01_background}
\input{sections/02_targets}
\input{sections/03_methodology}
\input{sections/04_experiments}
\input{sections/05_results_discussion}
\input{sections/06_limitations}
\input{sections/07_conclusion}

\bibliography{refs}
\bibliographystyle{template/iclr2026_template/iclr2026_conference}

\end{document}
